A Gentle Introduction into Structural Causal Models

### 2021-05-03 intro.Rmd
intro stuff

 |Method          | Action |  Example
|-----------------|---------------------------|------------------------|
| Prediction      | Observation/Co-occurrence | What happened...
| Intervention    | Do-manipulation           | What happens if ...
| Counterfactual  | Hypothetical Realities    | What would have happened if...

>>>>

\footnotesize
 |Method          | Action |  Example | ML Method | 
|---------------------|-------------|-------------------------|-------------------|
| Prediction $P(a|b)$               | Co-occurrence             | What happened...               | Supervised/Unsupervised  
| Intervention $P(a|do(b),c)$       | Do-manipulation           | What happens if ...            | Reinforcement Learning      
| Counterfactual $P(a_b|a`,b`)$     | Hypotheticals   | What would have happened if... | Reinforcement Learning/Interpretable ML

Table: Pearls Hierachy of Causation (2009)

\normalsize
